Learning constraints in tabular data

### 2016-05-20 Paper/ECAI/tabular.tex
Removed old text
minor changes

\usepackage{times}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[numbers]{natbib}
\usepackage{notoccite}
\usepackage{framed}
\usepackage{amsmath}
\usepackage{tabularx}
\usepackage{subcaption}

@@

Let us illustrate this on one of the spreadsheets from the gathered dataset. In Figure \ref{fig:autocompletion_example}, \sergey{to be finished}

>>>>

\usepackage{times}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[numbers]{natbib}
\usepackage{notoccite}
\usepackage{fixltx2e}
\usepackage{framed}
\usepackage{amsmath}
\usepackage{tabularx}
\usepackage{subcaption}

@@

Let us illustrate this on one of the spreadsheets from the gathered dataset. In Figure \ref{fig:autocompletion_example}, we see two tables the upper one is completed and in the lower one values in the last raw are not yet filled, then the system finds a satisfying constraint (\textit{SUMIF}) and based on it proposes filling values.
